DESING AND SIMULATION SOFTWARE FOR RHODOTRON TYPE ELECTRON ACCELERATORS

### 2023-09-19 subsections/simulation/intermediate_versions/intermediate.tex
enstitü versiyonu

\subsection{$\phi_{lag}$ Optimization For Bunches} \label{sec:philag_sweep}
After successfully accelerating single \e, particle bunches were implemented to approximate a real \e gun. 
They were modeled as $N$ electrons fired from an \e gun at even time intervals. This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsed \e gun design.

Addition of bunches would immediately proven useful when finding optimal phase lag for bunch entry.
$\phi_{lag}$ for a bunch was defined as the RF phase when the first \e of the bunch has entered the cavity and it defines the starting time of the current pass.
To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as
\begin{itemize}
    \item $\mu E$: Average energy,
    \item $E_{rms}$: Root mean square of energy,
    \item $R_{rms}$: Root mean square of \e positions.
\end{itemize}
Optimal $\phi_{lag}$ would produce maximum $\mu E$ while minimizing $E_{rms}$ \& $R_{rms}$. For the first pass, 
$E_{rms}$ and $R_{rms}$ would be vaguely dependent of each other; therefore, initial implementation of $\phi_{lag}$ sweep was based on minimizing $E_{rms}$ during simulation (\textit{see \fromfig{phlag_opt}}). 
For $\mu E$ considerations, data from the software would be analyzed either manually or by using external tools such as \textit{ROOT framework}. 
\begin{figure}[H]
    \centering
    %\captionsetup{justification=centering}
    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
        int phase_opt(int phase_sweep_range){
            double minrms = 1;
            int opt_phase;
            for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
              Bunch bunch1(RFphase);
              double t1 = 0;
              bunch1.bunch_gecis_t(t1);
              bunch1.reset_pos();

              if( bunch1.E_rms() < minrms ){
                minrms = bunch1.E_rms();
                opt_phase = RFphase;
              }
            }
            return opt_phase;
        }
    \end{minted}
    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design.}
    \label{fig:phlag_opt}
\end{figure}
Since $\phi_{lag}$ is relatively easy to change after production, another version of \fromfig{phlag_opt} that was modified for given magnet design parameters was also implemented (\textit{see \fromfig{phlag_opt_n_pass} in \fromapp{intermediate_codes}}). 
This version can be useful for optimizing $\phi_{lag}$ in case of production issues in magnets.

@@

Interaction logic for \eE and \eB in 3D can be found in \fromfig{3D_e_EM_interaction_first}.
\iffalse \begin{figure}[H]
    %\captionsetup[subfigure]{justification=centering}
    %\captionsetup{justification=centering}
    \begin{subfigure}{\textwidth}
        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
            vector3d CoaxialRFField::actOn(Electron& e){
                vector3d Efield = getField(e.pos);                          // Calculate E vector
                vector3d F_m = Efield*1E6*eQMratio;                         // Calculate F/m vector
                vector3d acc = (F_m - e.vel*(e.vel*F_m)/(c*c))/e.gamma();   // Calculate a vector
                return acc;
            }
        \end{minted}
    \end{subfigure}

    \begin{subfigure}{\textwidth}
        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
            vector3d MagneticField::actOn(Electron& e){
                if (isInside(e.pos) == -1)
                    return vector3d(0,0,0);
                vector3d Bfield = getField(e.pos);                          // Calculate B vector
                vector3d F_m = (e.vel % Bfield)*eQMratio;                   // Calculate F/m vector
                vector3d acc = (F_m)/e.gamma();                             // Calculate a vector
                return acc;
            }
        \end{minted}
    \end{subfigure}
    \caption{\eEM  interaction logic from \fromeq{acc_of_E_and_B}.}
    \label{fig:3D_e_EM_interaction_first}
\end{figure} \fi
\begin{figure}[H]
    %%\captionsetup[subfigure]{justification=centering}
    %%\captionsetup{justification=centering}
    \begin{minipage}{\textwidth}
        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
            vector3d CoaxialRFField::actOn(Electron& e){
                vector3d Efield = getField(e.pos);                          // Calculate E vector
                vector3d F_m = Efield*1E6*eQMratio;                         // Calculate F/m vector
                vector3d acc = (F_m - e.vel*(e.vel*F_m)/(c*c))/e.gamma();   // Calculate a vector
                return acc;
            }
        \end{minted}
    \end{minipage}

    \begin{minipage}{\textwidth}
        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
            vector3d MagneticField::actOn(Electron& e){
                if (isInside(e.pos) == -1)
                    return vector3d(0,0,0);
                vector3d Bfield = getField(e.pos);                          // Calculate B vector
                vector3d F_m = (e.vel % Bfield)*eQMratio;                   // Calculate F/m vector
                vector3d acc = (F_m)/e.gamma();                             // Calculate a vector
                return acc;
            }
        \end{minted}
    \end{minipage}
    \caption{\eEM  interaction logic from \fromeq{acc_of_E_and_B}.}
    \label{fig:3D_e_EM_interaction_first}
\end{figure}
Where * and \% are, dot-product and cross-product respectably. (\fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})

@@

These three methods were then tested in the same setup as \fromfig{mag_lf_render}. The results can be found in \fromfig{lf_rk1_rk2_comparison} of \fromapp{data_graph}.
\textit{RK4-1} was decided to be abandoned as it produced the same accuracy in twice the simulation time of \textit{RK4-2}.

More rigerous testing was done with \textit{Leap-frog} and \textit{RK4-2} however. 
Still using the setup in \fromfig{mag_lf_render}, each $dt$ configuration was simulated 10 times, calculating average and standard deviations afterwards.
Results from these tests can be observed in \fromfig{mag_lf_rk2_comparison}.
\iffalse \begin{figure}
    %\captionsetup[subfigure]{justification=centering}
    %\captionsetup{justification=centering}
    \centering
    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/analiz/mag_lf_rk2_dt-E.png}
        \caption*{$dt$ vs $\Delta E$}
    \end{subfigure}

    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/analiz/mag_lf_rk2_dt-Tsim.png}
        \caption*{$dt$ vs $T_{sim}$}
    \end{subfigure}
    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
    \label{fig:mag_lf_rk2_comparison}
\end{figure} \fi
\begin{figure}
    \centering
    \subfigure[\centering $dt$ vs $\Delta E$]{{\includegraphics[width=0.8\textwidth]{../../../figures/analiz/mag_lf_rk2_dt-E.png} }}%
    \qquad\subfigure[\centering $dt$ vs $T_{sim}$]{{\includegraphics[width=0.8\textwidth]{../../../figures/analiz/mag_lf_rk2_dt-Tsim.png} }}%
    \vspace{20pt}
    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns.}
    \label{fig:mag_lf_rk2_comparison}
\end{figure}
The data from these tests can be found in \fromtabs{lf_mag_table}{rk2_mag_table} of \fromapp{data_graph}.
To investigate the data further, one can define a performance measurement, $F$ as
\vspace{-10pt}\begin{eqnarray*}
    F &\propto& 1/T  , \\
    F &\propto& 1/\Delta E . 
\vspace{-10pt}\end{eqnarray*}
When $dt=10^{-5}$ ns was taken as reference point due to providing a good balance of accuracy and computational intensity, 
relative performance can be calculated as
\vspace{-10pt}\begin{eqnarray} \label{eq:f_lf_rk_mag_1}
    \Delta E_{LF} &=& 110 \times 10^{-5} MeV,\nonumber\\
    \Delta E_{RK}^1 &=& 64 \times 10^{-5} MeV,\nonumber\\
    T_{LF}^1 &=& 9.44 \pm 0.03 s, \nonumber\\
    T_{RK}^1 &=& 21.33 \pm 0.02 s, \nonumber\\
    \Delta E_{LF} \times T_{LF} &=& 104 \times 10^{-4} \pm 10^{-4} MeV s, \nonumber\\ %0.003
    \Delta E_{RK} \times T_{RK} &=& 137 \times 10^{-4} \pm 2\times 10^{-4}  MeV s, \nonumber\\ %0.001
    F_{LF}/F_{RK} &=& \frac{\Delta E_{RK} \times T_{RK} }{\Delta E_{LF} \times T_{LF}^1} = 1.32 \pm 0.01 .
\vspace{-10pt}\end{eqnarray}
Also, another relative performance can be obsered from the data as
\vspace{-10pt}\begin{eqnarray} \label{eq:f_lf_rk_mag_2}
    \Delta E_{LF} (dt=3 \times 10^{-5}) \approx \Delta E_{RK} (dt=5 \times 10^{-5}) &\approx& 32.5 \times 10^{-4} MeV, \nonumber\\
    T_{LF}(dt=3 \times 10^{-5})  &=& 3.18 \pm 0.02 s, \nonumber\\ %0.0032
    T_{RK}(dt=5 \times 10^{-5})  &=& 4.30 \pm 0.01 s, \nonumber\\ %0.0022
    F_{LF}/F_{RK} = \frac{T_{RK}(dt=5 \times 10^{-5})}{T_{LF}(dt=3 \times 10^{-5})} &=& 1.4 \pm 0.1.
\vspace{-10pt}\end{eqnarray}
Uncertainty of \fromeq{f_lf_rk_mag_2} was taken high due to the approximation. 
After combining \fromeqs{f_lf_rk_mag_1}{f_lf_rk_mag_2}, $F$ can be calculated as
\vspace{-10pt}\begin{equation}
    F_{LF}/F_{RK} = 1.36 \pm 0.05.
\vspace{-10pt}\end{equation}
Therefore, \textit{Leap-frog} was found to be the better choice as it provided with $1.36 \pm 0.05$ times accuracy in \eB interactions at a given time with respect to \textit{RK4}. However,
\textit{RK4} was promising in situations where decreasing the stepsize, $dt$, is not viable. Therefore both were integrated into \textit{Rhodotron Simulation} for the user to decide.
\textit{RK4-2} renders from these test can be found in \fromfig{mag_rk_render} of \fromapp{example_simulation_runs}.

@@

As test setups, two simulation confgurations were made. They aimed to test the accuracy of acceleration of a beam in parallel and perpendicular static uniform electric fields.
Both configurations had an \egun located at $(-0.753, 0, 0)$m, directed at $(1, 0, 0)$ firing electrons with the kinetic energy of $1$MeV. 
\iffalse \begin{figure}[H]
    \centering
    \begin{subfigure}{0.47\textwidth}
        \centering
        \includegraphics[width=0.9\linewidth]{../../../figures/illustrations/statE_1.png}
        \caption*{Setup-1 parallel $\vecthreeBF{E}$ field}
    \end{subfigure}
    \begin{subfigure}{0.48\textwidth}
        \centering
        \includegraphics[width=0.9\linewidth]{../../../figures/illustrations/statE_2.png}
        \caption*{Setup-2, perpendicular $\vecthreeBF{E}$ field}
    \end{subfigure}
    \caption{Illustration of test setups.}
\end{figure} \fi
\begin{figure}[H]
    \centering
    \subfigure[\centering Setup-1 parallel $\vecthreeBF{E}$ field]{{\includegraphics[width=0.423\textwidth]{../../../figures/illustrations/statE_1.png} }}%
    \qquad\subfigure[\centering Setup-2, perpendicular $\vecthreeBF{E}$ field]{{\includegraphics[width=0.432\textwidth]{../../../figures/illustrations/statE_2.png} }}%
    \vspace{20pt}
    \caption{Illustration of test setups.}
\end{figure}
In the first test, the beam would be injected into a static uniform electric field \\
$\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.

Considering the $\vecthreeBF{E}$ is parallel to the beam path, potential difference $V$ in the trejectory until \vecNum{-0.753}{0}{0}m is
\vspace{-10pt}\begin{eqnarray}
    \Delta V^1 &=& - \int \dotProdBF{E}{ds} \\
             &=& - \int_{-0.753}^{0.753} -2.65616 \times dx \\
             &=& 2.65616 \times 1.506 \\
             &=& 4 MV, \\
    \Delta E^1 &=& 4 MeV, \\
    E_{exitTH}^1 &=& 5 MeV.
\vspace{-10pt}\end{eqnarray}

In the second test on the other hand, the beam would be injected into a different static uniform electric field,
$\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
\vspace{-10pt}\begin{eqnarray}
    \Delta V^2   &=& - \int \dotProdBF{E}{ds} \\
                 &=& - \int_{0}^{0.753} -5.31232 \times dy \\
                 &=& 5.31232 \times 0.753 \\
                 &=& 4 MV, \\
    \Delta E^2   &=& 4 MeV, \\
    E_{exitTH}^2 &=& 5 MeV.
\vspace{-10pt}\end{eqnarray}

@@

The implemenation can be found in \fromfigf{_runMT}{fireAllWithFireTimesMT}{setupPool}{threadLoop} in \fromapp{intermediate_codes}.

>>>>

\subsection{$\phi_{lag}$ Optimization For Bunches} \label{sec:philag_sweep}
After successfully accelerating single \e, particle bunches were implemented to approximate a real \e gun. 
They were modeled as $N$ electrons fired from an \e gun at even time intervals. This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsed \e gun design.
\clearpage
Addition of bunches would immediately proven useful when finding optimal phase lag for bunch entry.
$\phi_{lag}$ for a bunch was defined as the RF phase when the first \e of the bunch has entered the cavity and it defines the starting time of the current pass.
To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as
\vspace{-10pt}\begin{itemize}
    \item $\mu E$: Average energy,
    \item $E_{rms}$: Root mean square of energy,
    \item $R_{rms}$: Root mean square of \e positions.
\end{itemize}

Optimal $\phi_{lag}$ would produce maximum $\mu E$ while minimizing $E_{rms}$ \& $R_{rms}$. For the first pass, 
$E_{rms}$ and $R_{rms}$ would be vaguely dependent of each other; therefore, initial implementation of $\phi_{lag}$ sweep was based on minimizing $E_{rms}$ during simulation (\textit{see \fromfig{phlag_opt}}). 
For $\mu E$ considerations, data from the software would be analyzed either manually or by using external tools such as \textit{ROOT framework}. 
\vspace{20pt}
\begin{figure}[H]
    \centering
    %\captionsetup{justification=centering}
    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
        int phase_opt(int phase_sweep_range){
            double minrms = 1;
            int opt_phase;
            for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
              Bunch bunch1(RFphase);
              double t1 = 0;
              bunch1.bunch_gecis_t(t1);
              bunch1.reset_pos();

              if( bunch1.E_rms() < minrms ){
                minrms = bunch1.E_rms();
                opt_phase = RFphase;
              }
            }
            return opt_phase;
        }
    \end{minted}
    \vspace{20pt}
    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design.}
    \label{fig:phlag_opt}
\end{figure}
\clearpage
Since $\phi_{lag}$ is relatively easy to change after production, another version of \fromfig{phlag_opt} that was modified for given magnet design parameters was also implemented (\textit{see \fromfig{phlag_opt_n_pass} in \fromapp{intermediate_codes}}). 
This version can be useful for optimizing $\phi_{lag}$ in case of production issues in magnets.

@@

Implementations for \eE and \eB interactions in 3D can be found in \fromfigs{3D_e_E_interaction_first}{3D_e_B_interaction_first}, 
where * and \% are, dot-product and cross-product respectably. (\fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})
\iffalse \begin{figure}[H]
    %\captionsetup[subfigure]{justification=centering}
    %\captionsetup{justification=centering}
    \begin{subfigure}{\textwidth}
        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
            vector3d CoaxialRFField::actOn(Electron& e){
                vector3d Efield = getField(e.pos);                          // Calculate E vector
                vector3d F_m = Efield*1E6*eQMratio;                         // Calculate F/m vector
                vector3d acc = (F_m - e.vel*(e.vel*F_m)/(c*c))/e.gamma();   // Calculate a vector
                return acc;
            }
        \end{minted}
    \end{subfigure}

    \begin{subfigure}{\textwidth}
        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
            vector3d MagneticField::actOn(Electron& e){
                if (isInside(e.pos) == -1)
                    return vector3d(0,0,0);
                vector3d Bfield = getField(e.pos);                          // Calculate B vector
                vector3d F_m = (e.vel % Bfield)*eQMratio;                   // Calculate F/m vector
                vector3d acc = (F_m)/e.gamma();                             // Calculate a vector
                return acc;
            }
        \end{minted}
    \end{subfigure}
    \caption{\eEM  interaction logic from \fromeq{acc_of_E_and_B}.}
    \label{fig:3D_e_EM_interaction_first}
\end{figure} \fi
\iffalse \vspace{20pt}
\begin{figure}[H]
    %%\captionsetup[subfigure]{justification=centering}
    %%\captionsetup{justification=centering}
    \begin{minipage}{\textwidth}
        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
            vector3d CoaxialRFField::actOn(Electron& e){
                vector3d Efield = getField(e.pos);                          // Calculate E vector
                vector3d F_m = Efield*1E6*eQMratio;                         // Calculate F/m vector
                vector3d acc = (F_m - e.vel*(e.vel*F_m)/(c*c))/e.gamma();   // Calculate a vector
                return acc;
            }
        \end{minted}
    \end{minipage}

    \begin{minipage}{\textwidth}
        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
            vector3d MagneticField::actOn(Electron& e){
                if (isInside(e.pos) == -1)
                    return vector3d(0,0,0);
                vector3d Bfield = getField(e.pos);                          // Calculate B vector
                vector3d F_m = (e.vel % Bfield)*eQMratio;                   // Calculate F/m vector
                vector3d acc = (F_m)/e.gamma();                             // Calculate a vector
                return acc;
            }
        \end{minted}
    \end{minipage}
    \vspace{20pt}
    \caption{\eEM  interaction logic from \fromeq{acc_of_E_and_B}.}
    \label{fig:3D_e_EM_interaction_first}
\end{figure}\fi
\begin{figure}[H]
    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
        vector3d CoaxialRFField::actOn(Electron& e){
            vector3d Efield = getField(e.pos);                        // Calculate E vector
            vector3d F_m = Efield*1E6*eQMratio;                       // Calculate F/m vector
            vector3d acc = (F_m - e.vel*(e.vel*F_m)/(c*c))/e.gamma(); // Calculate a vector
            return acc;
        }
    \end{minted}
    \vspace{20pt}
    \caption{\eE interaction logic from \fromeq{acc_of_E_and_B}.}
    \label{fig:3D_e_E_interaction_first}
\end{figure}
\vspace{20pt}
\begin{figure}[H]
        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
            vector3d MagneticField::actOn(Electron& e){
                if (isInside(e.pos) == -1)
                    return vector3d(0,0,0);
                vector3d Bfield = getField(e.pos);                        // Calculate B vector
                vector3d F_m = (e.vel % Bfield)*eQMratio;                 // Calculate F/m vector
                vector3d acc = (F_m)/e.gamma();                           // Calculate a vector
                return acc;
            }
        \end{minted}
    \vspace{20pt}
    \caption{\eB interaction logic from \fromeq{acc_of_E_and_B}.}
    \label{fig:3D_e_B_interaction_first}
\end{figure}

@@

These three methods were then tested in the same setup as \fromfig{mag_lf_render}. The results can be found in \fromfig{lf_rk1_rk2_comparison} of \fromapp{data_graph}.
\textit{RK4-1} was decided to be abandoned as it produced the same accuracy in twice the simulation time of \textit{RK4-2}.
\clearpage
\iffalse \begin{figure}
    %\captionsetup[subfigure]{justification=centering}
    %\captionsetup{justification=centering}
    \centering
    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/analiz/mag_lf_rk2_dt-E.png}
        \caption*{$dt$ vs $\Delta E$}
    \end{subfigure}

    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/analiz/mag_lf_rk2_dt-Tsim.png}
        \caption*{$dt$ vs $T_{sim}$}
    \end{subfigure}
    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
    \label{fig:mag_lf_rk2_comparison}
\end{figure} \fi
\begin{figure}[h]
    \centering
    \subfigure[\centering $dt$ vs $\Delta E$]{{\includegraphics[width=0.8\textwidth]{../../../figures/analiz/mag_lf_rk2_dt-E.png} }}%
    \qquad\subfigure[\centering $dt$ vs $T_{sim}$]{{\includegraphics[width=0.8\textwidth]{../../../figures/analiz/mag_lf_rk2_dt-Tsim.png} }}%
    \vspace{20pt}
    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns.}
    \label{fig:mag_lf_rk2_comparison}
\end{figure}
More rigorous testing was done with \textit{Leap-frog} and \textit{RK4-2} however. 
Still using the setup in \fromfig{mag_lf_render}, each $dt$ configuration was simulated 10 times, calculating average and standard deviations afterwards.

Example renders from these tests can be observed in \fromfig{mag_lf_rk2_comparison} and
the data from these tests can be found in \fromtabs{lf_mag_table}{rk2_mag_table} of \fromapp{data_graph}.
To investigate the data further, one can define a performance measurement, $F$ as
\vspace{-10pt}\begin{eqnarray}
    F &\propto& 1/T  , \\
    F &\propto& 1/\Delta E . 
\vspace{-10pt}\end{eqnarray}
When $dt=10^{-5}$ ns was taken as reference point due to providing a good balance of accuracy and computational intensity, 
relative performance can be calculated as
\vspace{-10pt}\begin{eqnarray} \label{eq:f_lf_rk_mag_1}
    \Delta E_{LF} &=& 110 \times 10^{-5} MeV,\\
    \Delta E_{RK}^1 &=& 64 \times 10^{-5} MeV,\\
    T_{LF}^1 &=& 9.44 \pm 0.03 s, \\
    T_{RK}^1 &=& 21.33 \pm 0.02 s, \\
    \Delta E_{LF} \times T_{LF} &=& 104 \times 10^{-4} \pm 10^{-4} MeV s, \\ %0.003
    \Delta E_{RK} \times T_{RK} &=& 137 \times 10^{-4} \pm 2\times 10^{-4}  MeV s, \\ %0.001
    F_{LF}/F_{RK} &=& \frac{\Delta E_{RK} \times T_{RK} }{\Delta E_{LF} \times T_{LF}^1} = 1.32 \pm 0.01 .
\vspace{-10pt}\end{eqnarray}
Also, another relative performance can be obsered from the data as
\vspace{-10pt}\begin{eqnarray} \label{eq:f_lf_rk_mag_2}
    \Delta E_{LF} (dt=3 \times 10^{-5}) \approx \Delta E_{RK} (dt=5 \times 10^{-5}) &\approx& 32.5 \times 10^{-4} MeV, \\
    T_{LF}(dt=3 \times 10^{-5})  &=& 3.18 \pm 0.02 s, \\ %0.0032
    T_{RK}(dt=5 \times 10^{-5})  &=& 4.30 \pm 0.01 s, \\ %0.0022
    F_{LF}/F_{RK} = \frac{T_{RK}(dt=5 \times 10^{-5})}{T_{LF}(dt=3 \times 10^{-5})} &=& 1.4 \pm 0.1.
\vspace{-10pt}\end{eqnarray}
Uncertainty of \fromeq{f_lf_rk_mag_2} was taken high due to the approximation. 
After combining \fromeqs{f_lf_rk_mag_1}{f_lf_rk_mag_2}, $F$ can be calculated as
\vspace{-10pt}\begin{equation}
    F_{LF}/F_{RK} = 1.36 \pm 0.05.
\vspace{-10pt}\end{equation}
Therefore, \textit{Leap-frog} was found to be the better choice as it provided with $1.36 \pm 0.05$ times accuracy in \eB interactions at a given time with respect to \textit{RK4}. However,
\textit{RK4} was promising in situations where decreasing the stepsize, $dt$, is not viable. Therefore both were integrated into \textit{Rhodotron Simulation} for the user to decide.
\textit{RK4-2} renders from these test can be found in \fromfig{mag_rk_render} of \fromapp{example_simulation_runs}.

@@

As test setups, two simulation confgurations were made. They aimed to test the accuracy of acceleration of a beam in parallel and perpendicular static uniform electric fields.
Both configurations had an \egun located at $(-0.753, 0, 0)$m, directed at $(1, 0, 0)$ firing electrons with the kinetic energy of $1$MeV. 
\iffalse \begin{figure}[H]
    \centering
    \begin{subfigure}{0.47\textwidth}
        \centering
        \includegraphics[width=0.9\linewidth]{../../../figures/illustrations/statE_1.png}
        \caption*{Setup-1 parallel $\vecthreeBF{E}$ field}
    \end{subfigure}
    \begin{subfigure}{0.48\textwidth}
        \centering
        \includegraphics[width=0.9\linewidth]{../../../figures/illustrations/statE_2.png}
        \caption*{Setup-2, perpendicular $\vecthreeBF{E}$ field}
    \end{subfigure}
    \caption{Illustration of test setups.}
\end{figure} \fi
\vspace{20pt}
\begin{figure}[H]
    \centering
    \subfigure[\centering Setup-1 parallel $\vecthreeBF{E}$ field]{{\includegraphics[width=0.423\textwidth]{../../../figures/illustrations/statE_1.png} }}%
    \qquad\subfigure[\centering Setup-2, perpendicular $\vecthreeBF{E}$ field]{{\includegraphics[width=0.432\textwidth]{../../../figures/illustrations/statE_2.png} }}%
    \vspace{20pt}
    \caption{Illustration of test setups.}
\end{figure}
\clearpage
In the first test, the beam would be injected into a static uniform electric field \\
$\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
Considering the $\vecthreeBF{E}$ is parallel to the beam path, beam energy at exit can be calculated as
\vspace{-10pt}\begin{eqnarray}
    \Delta V^1 &=& - \int \dotProdBF{E}{ds} \nonumber\\
             &=& - \int_{-0.753}^{0.753} -2.65616 \times dx \nonumber\\
             &=& 2.65616 \times 1.506 \nonumber\\
             &=& 4 MV, \\
    \Delta E^1 &=& 4 MeV, \\
    E_{exitTH}^1 &=& 5 MeV.
\vspace{-10pt}\end{eqnarray}

In the second test on the other hand, the beam would be injected into a different static uniform electric field,
$\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
Beam energy at exit can be calculated as
\vspace{-10pt}\begin{eqnarray}
    \Delta V^2   &=& - \int \dotProdBF{E}{ds} \nonumber \\
                 &=& - \int_{0}^{0.753} -5.31232 \times dy \nonumber \\
                 &=& 5.31232 \times 0.753 \nonumber \\
                 &=& 4 MV, \\
    \Delta E^2   &=& 4 MeV, \\
    E_{exitTH}^2 &=& 5 MeV.
\vspace{-10pt}\end{eqnarray}

@@

The implemenation of multithreading can be found in \fromfigf{_runMT}{fireAllWithFireTimesMT}{setupPool}{threadLoop} in \fromapp{intermediate_codes}.

### 2023-09-19 subsections/simulation/poc/poc.tex
enstitü versiyonu

%%%%%%
% Start of poc.tex
\section{Proof of Concept}
The POC worked with interacting an electron with the EM field provided, at discrete time steps $dt$. The core sequence of this software is provided below.
Where $\vecthreeBF{r}$ is the position, $\vecthreeBF{v}$ is the velocity of the $e^-$;
\begin{itemize}
    \item Get electron energy $E_{in}$,
    \item Get the RF field definitions,
    \item Get the magnet design parameters if there is any,
    \item Do following until the simulation time has ellapsed,
    \begin{enumerate}
        \item Calculate $\vecthreeBF{E}_{||}$($\vecthreeBF{r}$),
        \item Calculate $\vecthreeBF{a}_{E ||}$ using \fromeq{para_and_perp_acc_of_lorentz_force},
        \item Calculate $\vecthreeBF{r}$($t+dt$) using \fromeq{leapfrog_sync_x},
        \item Calculate $\vecthreeBF{v}$($t+dt$) using \fromeq{leapfrog_sync_v},
        \item Calculate new $E_t$.
    \end{enumerate}
\end{itemize}
The implemenation of this logic can be observed in \fromfig{POC_core_logic}. 
\begin{figure}[H]
    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
        for (double t=0; t<SimuTime; t+=dT){
            double RelBeta  = v/c;
            double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);

@@

            RelBeta  = v/c;
            RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
            Et=RelGamma*E0; 
        }
    \end{minted}
    \caption{Core logic loop of the POC.}
    \label{fig:POC_core_logic}
\end{figure}
After simulating the \textit{synchronous electron} mentioned in \fromsec{cavity_of_a_rhodotron} 
with $\phi_{lag}=15^\circ$, $P_{diss}=40$kW, $R_1=0.188$m, $R_2=0.753$m, $f=107.5$MHz for one pass, 
the results from \textit{POC}, \textit{CST} and \fromeq{W_gain_each_pass_pottier} were found to be
% 40 kW total power
% Emax = 0.96 in old, 2.08 in new version
% R1 = 0.1882
% R2 = 0.753
% f = 107.5
\vspace{-10pt}\begin{eqnarray}
    E_{Pottier} &=& 0.593 MeV  , \nonumber\\
    E_{CST} &=& 0.521 MeV  ,  \label{eq:poc_E_results}\\
    E_{POC} &=& 0.532 MeV . \nonumber
\vspace{-10pt}\end{eqnarray}

>>>>

%%%%%%
% Start of poc.tex
\section{Proof of Concept}
The proof of concept (POC) worked with interacting an electron with the EM field provided, at discrete time steps $dt$. 
The core sequence of this software is provided below and the implemenation of this logic can be observed in \fromfig{POC_core_logic}. 
Where $\vecthreeBF{r}$ is the position, $\vecthreeBF{v}$ is the velocity of the $e^-$:
\begin{itemize}
    \item Get electron energy $E_{in}$,
    \item Get the RF field definitions,
    \item Get the magnet design parameters if there is any,
    \item Do following until the simulation time has ellapsed,
    \begin{enumerate}
        \item Calculate $\vecthreeBF{E}_{||}$($\vecthreeBF{r}$),
        \item Calculate $\vecthreeBF{a}_{E ||}$ using \fromeq{para_and_perp_acc_of_lorentz_force},
        \item Calculate $\vecthreeBF{r}$($t+dt$) using \fromeq{leapfrog_sync_x},
        \item Calculate $\vecthreeBF{v}$($t+dt$) using \fromeq{leapfrog_sync_v},
        \item Calculate new $E_t$.
    \end{enumerate}
\end{itemize}
\clearpage
\begin{figure}[H]
    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
        for (double t=0; t<SimuTime; t+=dT){
            double RelBeta  = v/c;
            double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);

@@

            RelBeta  = v/c;
            RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
            Et=RelGamma*E0; 
        }
    \end{minted}
    \vspace{20pt}
    \caption{Core logic loop of the POC.}
    \label{fig:POC_core_logic}
\end{figure}

After simulating the \textit{synchronous electron} mentioned in \fromsec{cavity_of_a_rhodotron} 
with $\phi_{lag}=15^\circ$, $P_{diss}=40$kW, $R_1=0.188$m, $R_2=0.753$m, $f=107.5$MHz for one pass, 
the results from \textit{POC}, \textit{CST} and \fromeq{W_gain_each_pass_pottier} were found to be
% 40 kW total power
% Emax = 0.96 in old, 2.08 in new version
% R1 = 0.1882
% R2 = 0.753
% f = 107.5
\vspace{-10pt}\begin{eqnarray}
    E_{Pottier} &=& 0.593 MeV  , \\
    E_{CST} &=& 0.521 MeV  ,  \label{eq:poc_E_results}\\
    E_{POC} &=& 0.532 MeV . 
\vspace{-20pt}\end{eqnarray}
